\resumeSubHeadingListStart

    \resumeSubheading
    {Heriot-Watt University, School of Mathematics \& CS}{Edinburgh, UK}
    {Internship, Machine Learning}{Apr 2024 \textbf{--} Sep 2024}
    \resumeItemListStart
        \resumeItem{``Deep unfolded networks for generative models'', supervised by Audrey Repetti.}
        \resumeItem{Studied in depth unfolded networks for dual forward-backward algorithm, based on \href{https://eurasip.org/Proceedings/Eusipco/Eusipco2022/pdfs/0000957.pdf}{Repetti et al. (2022)}.}
        \resumeItem{Researched denoising diffusion probabilistic models (DDPM) and improved variants, based on \href{https://arxiv.org/abs/2006.11239}{Ho et al. (2020)} and \href{https://arxiv.org/abs/2102.09672}{Nichol \& Dhariwal (2021)}.}
        \resumeItem{Conducted extensive study of DDPM training scheme to optimize an unfolded network of approximately 10k parameters.}
        \resumeItem{Attended conferences and seminars on inverse problems and generative models at the Maxwell Institute of the University of Edinburgh.}
    \resumeItemListEnd

    \resumeSubheading
    {INRIA - MAGNET team}{Lille, France}
    {Internship, Machine Learning}{Mar 2022 \textbf{--} Aug 2022}
    \resumeItemListStart
        \resumeItem{``Fairness in Federated Learning'', supervised by Michael Perrot.}
        \resumeItem{Produced an in-depth taxonomy of the existing federated and fairness-enforcing algorithms.}
        \resumeItem{Proposed and implemented a novel approach based on a weighting gradients scheme.}
        \resumeItem{Attended conferences and seminars on subjects related to federated learning, differential privacy, and fairness in machine learning.}
    \resumeItemListEnd

\resumeSubHeadingListEnd