\resumeSubHeadingListStart

    \resumeSubheading
    {Stereolabs}{Paris, France}
    {Full-time, Research Engineer}{Oct 2024 \textbf{--} Nov 2025}
    \resumeItemListStart
        \resumeItem{Worked on projects related to neural stereo matching and semantic understanding applications.}
        \resumeItem{Implemented a codebase to train and evaluate models, from experimentation to production.}
        \resumeItem{Designed and implemented state-of-the-art approaches with a strong focus on latency, robustness and generalization.}
        \resumeItem{Conducted extensive experiments on the following topics: stereo matching, semantic segmentation, monocular depth, 3D foundation models, multi-task learning, Jetson-based inference, etc.}
    \resumeItemListEnd

    \resumeSubheading
    {Stereolabs}{Paris, France}
    {Internship, Research Engineer}{Apr 2023 \textbf{--} Aug 2023}
    \resumeItemListStart
        \resumeItem{Conducted comprehensive analysis of neural stereo matching across architecture design, optimization strategies, and data processing pipelines.}
        \resumeItem{Performed extensive literature review of over 30 research papers to contribute to technology watch and identify state-of-the-art approaches.}
    \resumeItemListEnd

\newpage

    \resumeSubheading
    {Euratechnologies}{Lille, France}
    {Internship, Data Scientist}{Sep 2021 \textbf{--} Feb 2022}
    \resumeItemListStart
        \resumeItem{\textbf{Project 1:}
        Bots detection in a MMO video game (Event2Vec and Attention-based LSTM).}
        \resumeItem{\textbf{Project 2:}
        Detection of defects on railway rails (YOLO architecture).}
        \resumeItem{\textbf{Project 3:}
        Multivariate and multi-steps sales forecasting (LSTM).}
    \resumeItemListEnd

\resumeSubheading
    {Helean}{Paris, France}
    {Internship, Data Scientist}{Jul 2021 \textbf{--} Aug 2021}
    \resumeItemListStart
        \resumeItem{Improved their forecasting model using feature engineering and enriched their data with web scraping.}
    \resumeItemListEnd

\resumeSubHeadingListEnd